---
title: "`r paste('Stage Review', params$ss)`"
output: html_document
params:
    route_index: 4
    ss: SS1 / 2

#rmarkdown::render(input = "stage-test.Rmd",  output_file = "ss1-2.html", params= list(route_index = 3, ss = 'SS1 / 2' ))
---

*Automated stage reviews from `RallyDataJunkie.com`*

```{r setup, include=FALSE, echo=FALSE, message=FALSE, output=FALSE}

geojson_filename = 'data/finland_arctic_2021.geojson'

#route_index = 4 # 3, 4, 5, 6 

geojson_sf = sf::st_read(geojson_filename)
# Drop the Z dimension
geojson_sf = sf::st_zm(geojson_sf, drop = TRUE, what = "ZM")


route_index = params$route_index

source('code/sketches.R')
utm_routes = get_utm_projection(geojson_sf)

stage_route_gj = geojsonio::geojson_json(geojson_sf[route_index,]$geometry)

route_basis_sf = geojson_sf[route_index,]
route_basis_utm = utm_routes[route_index,]

stage_coords = as.data.frame(sf::st_coordinates(route_basis_sf))

dem <- get_dem(stage_coords)
dem_utm <- get_dem_utm(dem,geojson_sf)
```

```{r}
route_convexity <- get_route_convexity(route_basis_utm)

trj = create_trj(route_basis_utm)

# TO DO - route convexity needs trj integrations?
route_convexity = get_route_convexity2(route_convexity, dem_utm)

trj = create_trj(route_basis_utm)

trj_corners = trj[trj$firstish,]
trj_corners$corner_num = cumsum(trj_corners$firstish)

trj_segment_plots_list = trj_segments_plots(trj)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#trj$radius = curvatures(trj$x, lead(trj$x, 1), lead(trj$x,2),
#                        trj$y, lead(trj$y), lead(trj$y,2) )
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
trj$kmsection = 1 + trunc(trj$cum_dist/1000)
trj_gg_km = trj %>% group_by(kmsection) %>%
                  group_map(~seg_gg(.x))

trj_sinuosity_list = trj %>% group_by(kmsection) %>%
              group_map(~TrajSinuosity2(.x)) %>% unlist
trj_straightness_list = trj %>% group_by(kmsection) %>%
              group_map(~TrajStraightness(.x)) %>%
                unlist


trj_stats = data.frame(sinuosity=trj_sinuosity_list,
                       straightness = trj_straightness_list)

trj_stats$km = 1:max(trj$kmsection)

trj_stats$route = lapply(trj_gg_km, gt::ggplot_image)

```

## Stage Route Preview

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(leaflet)

leaflet() %>% 
  addProviderTiles("OpenTopoMap", group = "OSM") %>%
 addPolylines(color = "red", weight = 5,
               data=route_basis_sf)
```

Static map, significant corners highlighted:

```{r echo=FALSE, warning=FALSE, message=FALSE}
trj_route_plot(trj)
```

## Segmented Route

1km route sections, aligned to read left to right; significant corners highlighed.

```{r echo=FALSE, warning=FALSE, message=FALSE}
trj_segments_plot(trj_segment_plots_list, route_basis_sf)
```



## Elevation and Convexity Index into Route

Elevation and significant curvature vs distance into stage:

```{r echo=FALSE, warning=FALSE, message=FALSE}
elevation_convexity_plot(route_convexity, route_basis_sf,
                         signif_conv_index=0.1)
```

(Note that this uses a different curvature measure to the route plots; specifically, the curvature measure used here is the convexity index.)


```{r}
formattable(trj_stats[,c('km', 'sinuosity', 'straightness', 'route')], 
            list(sinuosity= color_tile( "transparent", "lightpink"),
                 straightness= color_tile("lightblue", "transparent")),
             caption=paste('Stage segmented into 1km sections:',
                           head(route_basis_sf, 1)$name))

```

