```{r}
knitr::opts_chunk$set(fig.path = paste0("images/stage-",i,"-"))
```

```{r route_config-{{route_i}}, results=FALSE, message=FALSE, warning=FALSE}
route_index = {{route_i}}
stage_route_gj = geojsonio::geojson_json(geojson_sf[route_index,]$geometry)

route_basis_sf = geojson_sf[route_index,]
route_basis_utm = utm_routes[route_index,]

stage_coords = as.data.frame(sf::st_coordinates(route_basis_sf))

dem <- get_dem(stage_coords)
dem_utm <- get_dem_utm(dem, geojson_sf)

route_convexity <- get_route_convexity(route_basis_utm)
route_convexity = get_route_convexity2(route_convexity, dem_utm)

trj = create_trj(route_basis_utm)

# Sample every 500m and select odd rows (mid point of km segment)
# Hack to resample against distance as time
trj$time = trj$cum_dist
sample_500m = TrajResampleTime(trj, 500 )[c(TRUE,FALSE),]
sample_5km = TrajResampleTime(trj, 5000 )
# Add kilometer labels
sample_500m$km = 1:nrow(sample_500m)
sample_5km$km = 5*(1:nrow(sample_5km))

trj_corners = trj[trj$firstish,]
trj_corners$corner_num = cumsum(trj_corners$firstish)

trj_segment_plots_list = trj_segments_plots(trj)

trj$kmsection = 1 + trunc(trj$cum_dist/1000)
trj_gg_km = trj %>% group_by(kmsection) %>%
                  group_map(~seg_gg(.x))

# In Rally Kenya, some sections were over 1km long
# which meant that some kilometer segments could be missed
# We need to resample if trj$distance > 1000
trj_sinuosity_list = trj %>% group_by(kmsection) %>%
              group_map(~TrajSinuosity2(.x)) %>% unlist
trj_straightness_list = trj %>% group_by(kmsection) %>%
              group_map(~TrajStraightness(.x)) %>%
                unlist


trj_stats = data.frame(sinuosity=trj_sinuosity_list,
                       straightness = trj_straightness_list)

trj_stats$km = 1:max(trj$kmsection)

# This is the route map for each section
trj_stats$route = lapply(trj_gg_km, gt::ggplot_image)

route_name = geojson_sf[route_index,]$name
```

# `r route_name`

A quick review of the stage, detailing the overall route, the route in 1km sections, route elevation profile and route curvature profile.

## Stage Route Preview

```{r map-preview-{{route_i}}, echo=FALSE, message=FALSE, warning=FALSE}
library(leaflet)

leaflet() %>% 
  addProviderTiles("OpenTopoMap", group = "OSM") %>%
  addPolylines(color = "red", weight = 5,
               data=route_basis_sf)
```

Static map, significant corners highlighted:

```{r static-map-{{route_i}}, results = FALSE, message=FALSE, warning=FALSE}
#g = trj_route_plot(get_stage_data(geojson_sf,{{route_i}}))
g = trj_route_plot(trj)

#Ideally we add labels that don't overlap line
# Add km labels
g + ggrepel::geom_label_repel(data=sample_500m,
                              aes(x=x, y=y, label=paste0(km,'km')),
               nudge_x=10, nudge_y=10, size=2) +
              theme_light() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
#g
```

## Segmented Route

1km route sections, aligned to read left to right; significant corners highlighted.

```{r route_segmented-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
ncol = 5
g = trj_segments_plot(trj_segment_plots_list, route_basis_sf, ncol)
h = ceiling(length(trj_segment_plots_list)/ncol)
subchunkify(g, 2*h, 7, route_i)
```

## Speed Estimates

*Estimates of speed along the route according to a very simple acceleration model.*

```{r route_speed-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(devtools)
# The curvature function takes an arc defined over
# x and y coordinate lists

#circlefit, from pracma::
circlefit = function (xp, yp, fast = TRUE) 
{
    if (!is.vector(xp, mode = "numeric") || !is.vector(yp, mode = "numeric")) 
        stop("Arguments 'xp' and 'yp' must be numeric vectors.")
    if (length(xp) != length(yp)) 
        stop("Vectors 'xp' and 'yp' must be of the same length.")
    if (!fast) 
        warning("Option 'fast' is deprecated and will not be used!", 
            call. = FALSE, immediate. = TRUE)
    n <- length(xp)
    p <- qr.solve(cbind(xp, yp, 1), matrix(xp^2 + yp^2, ncol = 1))
    v <- c(p[1]/2, p[2]/2, sqrt((p[1]^2 + p[2]^2)/4 + p[3]))
    rms <- sqrt(sum((sqrt((xp - v[1])^2 + (yp - v[2])^2) - v[3])^2)/n)
    #cat("RMS error:", rms, "\n")
    return(v)
}

curvature = function(x,y){
  #729181.8, 729186.1, 729190.4
  #4957667 , 4957676, 4957685
  tryCatch({
      # circlefit gives an error if we pass a straight line
      # Also hide the print statement in circlefit
      # circlefit() returns the x and y coords of the circle center
      # as well as the radius of curvature
      # We could then also calculate the angle and arc length
      circlefit(x,y)[3]
    },
    error = function(err) { 
      # For a straight, return the first co-ord and Inf diameter
      # Alternatively, pass zero diameter?
      c(x[1], y[1], Inf)[3]})
}

curvature2 = function(x1, x2, x3, y1, y2, y3){
  curvature(c(x1, x2, x3), c(y1, y2, y3))
}

# The base::Vectorize function provides a lazy way of 
# vectorising a non-vectorised function
curvatures = Vectorize(curvature2)
```


```{r route_convexity-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(dplyr)
  
route_convexity$radius = curvatures(lag(route_convexity$Midpoint_X), 
                                    route_convexity$Midpoint_X,
                                    lead(route_convexity$Midpoint_X),
                                    lag(route_convexity$Midpoint_Y),
                                    route_convexity$Midpoint_Y,
                                    lead(route_convexity$Midpoint_Y)
                                    )

invisible_bins = c(0, 10, 15, 20, 27.5, 35,
                    45, 60, 77.5, 100, 175, Inf)

route_convexity$invisible_ts = cut(route_convexity$radius,
                                   breaks = invisible_bins,
                                   labels = 1:(length(invisible_bins)-1),
                                   ordered_result=TRUE)

# Speeds in km/h
invisible_speeds = c(10, 40, 50, 60, 70, 80,
                     95, 110, 120, 130, 145)


route_convexity$invisible_sp = cut(route_convexity$radius,
                                   breaks = invisible_bins,
                                   labels = invisible_speeds,
                                   ordered_result=TRUE)

# Cast speed as factor, via character, to integer
route_convexity$invisible_sp = as.integer(as.character(route_convexity$invisible_sp))

route_convexity$invisible_time = 10/ (route_convexity$invisible_sp * 1000 /3600)


#duration = sum(route_convexity$invisible_time) 

# Acceleration model
sp = route_convexity$invisible_sp
sp[1] = 30 # nominal starting speed

# Crude acceleration / brake weights
acc = 1
dec = 1
for (i in 2:(length(sp)-1)) {
  # Accelerate up
  if (sp[i-1]<=sp[i]) sp[i] = (sp[i-1] + acc * sp[i]) / (1+acc)
                                  
  # Decelerate down
  if (sp[i]>sp[i+1]) sp[i] = (dec * sp[i] + sp[i+1]) / (1+dec)
}


route_convexity$acc_sp = sp
route_convexity$acc_sp[length(sp)] = route_convexity$invisible_sp[length(sp)]

# New time model
route_convexity$invisible_time2 = 10/ (route_convexity$acc_sp * 1000 /3600)

route_convexity = route_convexity %>% mutate(segment_sp = dist/invisible_time2)

# So now we need to generate kilometer marks and find time over each
route_convexity$kmsection = 1 + trunc(route_convexity$MidMeas/1000)
```

Kilometer section speeds (*kmtime* is time in seconds to complete that segment; *avspeed* is in km/h):

```{r route_convxity_table-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE}
route_convexity_gg_km = route_convexity %>% group_by(kmsection) %>%
                  summarise(section_length = sum(dist, na.rm=TRUE)/1000,
                            km_time = sum(invisible_time2),
                            av_speed = section_length * 3600/km_time,
                            maxspeed = max(acc_sp))
kable(route_convexity_gg_km)
```


```{r stage_time_estimate-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
duration2 = sum(route_convexity$invisible_time2) 
cat(paste0("Anticipated stage time: ", duration2 %/% 60, 'm ', round(mod(duration2, 60),1), 's' ))

```


Speed profile chart: this chart shows the anticipated speed over distance into route on a per kilometer basis (the green area is flat out, the pink is the sort of slow you see at a hairpin):

```{r route_conv_segement_plot-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

route_conv_segments_plots =function(rc, x="MidMeas", y="acc_sp"){
  # Create a list to hold each plot as a separate item
  segment_plots = list()

  for (i in 1:max(rc$kmsection)){
    # Add each plot to the plot list
    segment_plots[[length(segment_plots) + 1]] <-
      ggplot(rc[rc$kmsection==i,]) +
      annotate("rect", xmin=-Inf, xmax=Inf, ymin=0, ymax=30, alpha=0.15, fill='pink') + annotate("rect", xmin=-Inf, xmax=Inf, ymin=130, ymax=Inf, alpha=0.15, fill='green') +
      geom_line(aes_string(x=x, y=y)) +
      ylim(0,150) + theme_void() + ggtitle(paste0(i))
  }
  segment_plots
}

g2 = trj_segments_plot(route_conv_segments_plots(route_convexity), route_basis_sf, ncol)
subchunkify(g2, 2*h, 7, route_i)
```
```{r}
simple_segments_plots =function(rc, x="MidMeas", y="elevation"){
  # Create a list to hold each plot as a separate item
  segment_plots = list()

  for (i in 1:max(rc$kmsection)){
    # Add each plot to the plot list
    segment_plots[[length(segment_plots) + 1]] <-
      ggplot(rc[rc$kmsection==i,]) +
      geom_line(aes_string(x=x, y=y)) +
      theme_void() + ggtitle(paste0(i))
  }
  segment_plots
}
elev_plots_list = simple_segments_plots(route_convexity,y='elevation')
```



## Elevation and Convexity Index into Route

Elevation and significant curvature vs distance into stage:

```{r elev_complexity_plot-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE}
elevation_convexity_plot(route_convexity, route_basis_sf,
                         signif_conv_index=0.1) +
              labs(subtitle = paste0("Elevation and significant curvature plot"), x="Distance into stage (km)", y="Elevation (m)",
            caption = "Created by: RallyDataJunkie.com") +
                         theme_light() + theme(aspect.ratio=1/3)

# TO DO kilometer sections for elevation
# TO DO Text report by kilometer section
```

(Note that this uses a different curvature measure to the route plots; specifically, the curvature measure used here is the convexity index.)

Elevation delta signature — order the severity of height changes over each 10m section of the stage:

```{r elev_profile-{{route_i}}}
route_convexity = route_convexity %>% 
  mutate(elevation_delta= c(0,diff(elevation)))

route_convexity %>%
  arrange(elevation_delta) %>%
  mutate(dummy=row_number()) %>%
  ggplot(aes(x=dummy, y=abs(elevation_delta)))+geom_col() +
  theme_light() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + ylim(0, 7.5) +
      labs(title=paste0("Elevation Delta Profile for ", route_name))
```

Split section elevation profiles can be found in the stage km section summary table.

```{r elev_delta_sigs-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, results='asis' }

route_conv_segments_colbarplots_simple =function(rc, measure,
                                                 x=NULL,
                                                 ymax=7.5,
                                                 absval=FALSE,
                                                 negabs=FALSE){
  # Create a list to hold each plot as a separate item
  segment_plots = list()
  x = ifelse(is.null(x), 'dummy', x)
 
  if (negabs) {
    ymin = -abs(ymax)
    ymax= 0
    absval = TRUE
  } else if (absval)
    ymin = 0
  else
    ymin = -ymax

  
  for (i in 1:max(rc$kmsection)){
    # Add each plot to the plot list
    data = rc[rc$kmsection==i,] %>% 
              mutate(y= get(measure)) %>%
              arrange(y)
        
    if (x=='dummy')
      data = data %>% mutate(dummy=row_number()) %>% arrange(dummy)
  
    if (absval)
      data = data %>% mutate(y = abs(y))
    if (negabs) 
      data = data %>% mutate(y = -y)

    segment_plots[[length(segment_plots) + 1]] <-
      ggplot(data, aes_string(x=x)) +
      geom_col(aes(y=y)) + ylim(ymin, ymax)+
      theme_void() + 
      theme(panel.border = element_rect(colour = "grey", fill=NA, size=1)) +
      ggtitle(paste0(i))
  }
  segment_plots
}

# TO DO - ignore for now
#elev_delta_plots_list = route_conv_segments_colbarplots_simple(route_convexity, "elevation_delta", absval=TRUE)

# TO DO - suppress this plot and use as a column in km section table
#g2 = trj_segments_plot(elev_delta_plots_list, route_basis_sf, ncol)
#subchunkify(g2, 2*h, 7, route_i)
```


### Left and Right

How does the stage vary in terms of left and right turns?

Order the severity of right and left turns over each 10m section of the stage:

```{r left-right-{{route_i}} }
# Get a table of the left and right turns (eg ConvexityIndex)
route_convexity %>% 
  arrange(ConvexityIndex) %>%
  mutate(dummy=row_number()) %>%
  ggplot(aes(x=dummy, y=-abs(ConvexityIndex)))+geom_col()+ ylim(-1,0) +
  theme_light() + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
      labs(title=paste0("Corner Convexity Index Profile for ", route_name))

# TO DO - which is left and which is right?

# TO DO - kilometer sections for left and right
# TO DO Left/right text report by kilometer section
```

Kilometer segment convexity index signatures can be found in steg stage km section summary table.

```{r convexity_segment_sigs-{{route_i}}, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

route_conv_plot_list = route_conv_segments_colbarplots_simple(route_convexity, "ConvexityIndex", ymax=1, negabs=TRUE)
# TO DO - suppress this plot and use as a column in km section table
#g2 = trj_segments_plot(route_conv_plot_list, route_basis_sf, ncol)

#subchunkify(g2, 2*h, 7, route_i)
```


```{r longstraight-{{route_i}}}
# Straight lengths
route_convexity = route_convexity %>% mutate(startStraight = lag(!straightish, default=TRUE) & straightish) %>%
              mutate(strcount = cumsum(startStraight))

route_convexity$strcount[!route_convexity$straightish] = -1

straight_lengths = route_convexity %>% 
                        # We only want straightish segments...
                        dplyr::filter(strcount>=0) %>%
                        # Group by straight number
                        group_by(strcount)  %>%
                        # Find the length of each straight
                        summarize(strdistance = sum(dist))

longstraights = straight_lengths %>%
                        arrange( desc(strdistance) ) %>% head(5)

straights = route_convexity[!duplicated(route_convexity$strcount), ] %>%
                filter(strcount!=-1)

longstraights %>% 
    merge( straights, by=c('strcount')) %>%
  select(MidMeas, strdistance) %>%
  mutate(MidMeas = MidMeas/1000) %>%
  arrange(desc(MidMeas))  %>%
  rename("Distance into stage (km)"=MidMeas,
         "Straight length (m)"=strdistance) %>%
    formattable(caption=paste('Five longest straights (m)'))

# Need to merge in distance into stage
```

```{r long-straight-{{route_i}}}
ggplot(data=route_convexity,
       aes(x=Midpoint_X, y=Midpoint_Y)) + geom_path(color='grey', alpha=0.3) + coord_sf() +
       geom_point(data=route_convexity[(route_convexity$startStraight) & 
                           (route_convexity$strcount %in% longstraights$strcount),],
                  aes(x=Midpoint_X, y=Midpoint_Y), color='grey', size=0.1,  alpha=0.7) +
       geom_point(data=route_convexity[(!route_convexity$startStraight) & 
                           (route_convexity$strcount %in% longstraights$strcount),],
                  aes(x=Midpoint_X, y=Midpoint_Y), color='green', size=0.5, alpha=0.7) +
       geom_point(data=route_convexity[(route_convexity$firstish),],
                  aes(x=Midpoint_X, y=Midpoint_X), color='black', size=0.5) +
       theme_classic() +
       theme(axis.text.x = element_text(angle = 45)) 
```

### Sinuosity and Straightness

*Sinuosity and straightness are technical measures with specific defintions. They may or may not be that useful for route analysis in their current form. The intention is to try to find ways of identifying variously "interesting" kilometer stretches.*

```{r sinuosity-plot-{{route_i}}}
ggplot(trj_stats, aes(x=straightness,
                            y=sinuosity,
                            label = km)) + 
        geom_point(size=1)  +
        # hjust: left justification (0), right justification (1)
        geom_text(size=3, hjust = 1, nudge_y = -0.001) +
        ggtitle("Sinousity versus straightness")
```


```{r sinuosity_table-{{route_i}}, message=FALSE, warning=FALSE,}
trj_stats$elevationPlot = lapply(elev_plots_list, gt::ggplot_image)

#trj_stats$elevationDeltaProfile = lapply(elev_delta_plots_list, gt::ggplot_image)

trj_stats$convexityProfile = lapply(route_conv_plot_list, gt::ggplot_image)

formattable(trj_stats[,c('km', 'sinuosity', 'straightness',
                         'route', 'elevationPlot',
                         #'elevationDeltaProfile',
                         'convexityProfile')], 
            list(sinuosity= color_tile( "transparent", "lightpink"),
                 straightness= color_tile("lightblue", "transparent")),
             caption=paste('Stage segmented into 1km sections:',
                           head(route_basis_sf, 1)$name))

```



